Draft_Mid_Term

### 2022-10-06 Draft_Mid_Term.Rmd
Regression Updated
Regression model updated.

```{r summary_amenities_feature}
amenities_feature.list<-data %>% dplyr::select(
  starts_with('college_'),
  starts_with('daycare_'),
  starts_with('MedicalFacilities_'),
  starts_with('library_'),
  starts_with('hist_'),
  starts_with('church'),
  starts_with('park_'),
  starts_with('capital_'),
  price) %>% 
  st_drop_geometry()

@@

```{r}
sel.amenitie<-data %>% dplyr::select(
  starts_with('college_'),
  starts_with('daycare_'),
  starts_with('MedicalFacilities_'),
  starts_with('library_'),
  starts_with('hist_'),
  starts_with('church'),
  starts_with('capital_'),
  price) %>% 
  st_drop_geometry()
```

@@

tract_feature.list<-data[tract.list]%>% 
  st_drop_geometry()

@@

```{r}
names(nonnumeric)
```
```{r}
a = ls()
rm(list=a[which(a!='data' & a !='sel.internal.list' & a !='sel.tract.list' & a !='sel.amenitie')])
```

@@

nonnumeric <- data[nonnumeric.feature]%>% 
  st_drop_geometry()

@@

```{r}
M1 <- lm(price ~ ., data = nonnumeric)

```{r}
M2 <- lm(price ~ ., data = data[sel.internal.list])
```

```{r}
M3 <- lm(price ~ ., data = data[sel.tract.list])
```

```{r}
M4 <- lm(price ~., data = sel.amenitie)
```

>>>>

```{r summary_amenities_feature}
amenities_feature.list<-model_set %>% dplyr::select(
  starts_with('college_'),
  starts_with('daycare_'),
  starts_with('MedicalFacilities_'),
  starts_with('library_'),
  starts_with('hist_'),
  starts_with('church'),
  starts_with('park_'),
  starts_with('capital_'),
  price) %>% 
  st_drop_geometry()

@@

```{r}
sel.amenitie<-model_set%>% dplyr::select(
  starts_with('college_'),
  starts_with('daycare_'),
  starts_with('MedicalFacilities_'),
  starts_with('library_'),
  starts_with('hist_'),
  starts_with('church'),
  starts_with('capital_'),
  price) %>% 
  st_drop_geometry()
```

@@

tract_feature.list<-model_set[tract.list]%>% 
  st_drop_geometry()

@@

```{r}
names(nonnumeric)
```
```{r}
a = ls()
rm(list=a[which(a!='data' & a !='sel.internal.list' & a !='sel.tract.list' & a !='sel.amenitie' & a!='challenge_set'& a!= 'model_set')])
```

@@

nonnumeric <- model_set %>% dplyr::select(nonnumeric.feature1)%>% 
  st_drop_geometry()

@@

```{r}
M1 <- lm(price ~ ., data = nonnumeric)
```

```{r}
summary(M1)
```

```{r}
sel.internal<-model_set %>% dplyr::select(sel.internal.list) %>% st_drop_geometry()

M2 <- lm(price ~ ., data = sel.internal)
```
```{r}
summary(M2)
```

```{r}
sel.tract<-model_set %>% dplyr::select(sel.tract.list) %>% st_drop_geometry()
M3 <- lm(price ~ ., data = sel.tract)

summary(M3)
```

```{r}
M4 <- lm(price ~., data = sel.amenitie)

summary(M4)
```
